### 2021-02-11 abstract.tex
update abstract and introduction

\begin{abstract}
Due to the popularization of Android and the full range of applications (apps) targeting this platform, many security issues have emerged, attracting researchers and practitioners' attention. As such, many techniques for addressing security Android issues appeared, including approaches for mining sandboxes. Previous research studies have compared Android test case generation tools for this specific goal. Our research aims to explore new techniques for mining sandboxes, especially we are interested in understanding the limits of both static and dynamic analysis in this process. Although the use of test generation tools for mining sandboxes has been explored before, the potential to combine static analysis and dynamic analysis has not been sufficiently investigated yet. That is, in this paper, we will investigate the hypothesis that combining static and dynamic analysis techniques increases the process of mining Android sandboxes. To understand the bound of this combination, we conducted a non-exact replication of a previous study to detect what is the role of each of these analyses in malware detection using mining sandboxes. Like the original studies, we used DroidFax, a tool that instruments Android apps and collects relevant information about their execution (using the test case generation tools). DroidFax also executes static analysis that collects code coverage information and a set of sensitive APIs used by a given app during test execution. Our results demonstrate that analysis static has an important contribution to the mining sandboxes process, and his combination with dynamic analysis has the potential to improve malware detection techniques.

>>>>

\begin{abstract}
The popularization of Android platform and the growth number of Android apps that manage sensitive data, brought several security threats. During the last years researchers and practitioners have investigated techniques addressing security Android issues, including techniques that leverage dynamic analysis to mine Android Sandboxes. Mining sandboxes through test generation tool is not new, and has been investigated before, however a potential combination with static analysis has not been sufficiently explored.

In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. To this end, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compare the results of test case generation for mining sandboxes, isolating all possible effects of the static analysis on the results, that could leverage the original results. We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.

Our results demonstrate that analysis static has an important contribution to the mining sandboxes process, and his combination with dynamic analysis has the potential to improve malware detection techniques.

### 2021-02-11 introduction.tex
update abstract and introduction

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices\kn{citation for android being the most popular?}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} \kn{source and sink arrives out of nowhere in introduction. Either rephrase into a simpler term please or define those in a sentenc before.} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes~ \kn{A small sentence defining sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods \kn{in an Android app?}, using different approaches for automatically testing Android apps. These tools \kn{these analysis? because tools was not a word used before}, explore apps behavior and record all calls to sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules. \kn{This paragraph attempts to explain what a sandbox does and what it is dependent on, but the overall picture is still not clear. Consider defining sandbox in one sentence in previous paragraph, and in this paragraph use more concise terms like "Given an App A, with sensitive calls Set\_s, a Sanxbox Y does .....}

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
\kn{The rest of the paper is organized as follows...}

>>>>

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes. Given an app A, a sandbox S identifies sensitive resources access by app A, during dynamic analysis, and then block calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods in a Android app, using different approaches for automatically testing Android apps. These analysis explore apps behavior and record all calls to sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 describes all the apps malware used in our experiment, presenting their characterization. Section 4 introduces the study setting of our research. Section 5 presented some results, highlighting some motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.
